### 2016-05-24 paper/paper.tex
Open source software!
Revision pass

In this paper, we present DDoSCoin, which is a cryptocurrency with a
\emph{malicious} proof-of-work. DDoSCoin allows miners to prove that they have
contributed to a distributed denial of service attack against specific target
servers.  This proof involves making a large number of TLS connections to a
target server, and using infrequent cryptographic responses to prove that a
large number of connections has been made. Like proof-of-work puzzles, these
proofs are inexpensive to verify, and can be made arbitrarily difficult to
solve.

@@

Cryptocurrencies rely on proofs-of-work (PoW) that require miners to spend a
large amount of effort to solve a specific puzzle.  Solutions to these puzzles,
on the other hand, are designed to be inexpensive to verify. In Bitcoin, the
proof-of-work is a computational puzzle based on the SHA256 hash function, and
miners are tasked with finding a partial preimage. The best way to do this is to
iterate over a large number of inputs to the hash function, and check if the
output hash satisfies the partial preimage target. In simplified terms, to find
an input that hashes to N bits of 0s, the miner must perform on average $2^{N}$
hashes. Once such an input is found, other miners and Bitcoin nodes can verify the
puzzle solution with a single hash~\footnote{Bitcoin uses double-SHA256 in its
design, but this detail is not important for the purposes of this paper.}.

@@

Many see this distributed computation as a colossal waste of CPU resources, and
researchers have proposed alternative cryptocurrencies (altcoins) that aim to
have more beneficial proofs-of-work~\cite{primecoin,permacoin} that provide
utility beyond securing the underlying currency, such as finding chains of
large primes or proving the archive of data. In this paper however, we
investigate going in the opposite direction, and propose an altcoin that has a
\emph{malicious} proof-of-work that is externally detrimental.

In particular, we propose a proof-of-work that allows miners to prove they have
participated in a distributed denial of service (DDoS) attack against a
particular target. Miners are incentivized to send and receive large amounts of network
traffic at the target in order to produce a valid proof-of-work. As in other
cryptocurrencies, these proofs can be inexpensively verified by others, and the
original miner can collect a reward. This reward can be sold for other
currencies (including Bitcoin or even traditional currencies), allowing botnet
owners and other attacks to directly collect revenue for their assistance
in a decentralized DDoS attack.

The malicious ``proof-of-DDoS'' operates by having miners create a large number of
TLS connections to a target webserver, and using the server's signed responses
as a proof of connection. In modern versions of TLS, the server signs a
client-provided parameter of the connection, along with server-provided values
used in the key exchange of the connection. This allows the client to prove to
others that it has communicated with the server. In addition, the signed value
returned by the server is not predictable to the client, and is randomly
distributed. Thus, clients can use a similar trick as in Bitcoin, and only
report connections that match some rare threshold, such as the signature from
the server starts with $N$ bits of 0s. On average, it will take clients $2^{N}$
connections to produce such a proof.

@@

\emph{Contributions}
\begin{itemize}
\item Propose a novel conceptual cryptocurrency, DDoSCoin, whose proof-of-work
incentives miners to participate in a DDoS attack, and allows them prove they have done so.
\item Describe a way for target victims to be chosen by consensus of its
participants.
\item Implement our proof-of-work function and evaluate its performance and
impact.
\item Discuss several defenses against such a cryptocurrency that potential
victims can employ.
\end{itemize}

@@

Many alternate cryptocurrency protocols (altcoins) have been proposed since the
creation of Bitcoin. Although none have yet eclipsed the popularity of Bitcoin,
many altcoins have interesting innovations, often in the form of alternate
proof-of-work. For example, Litecoin uses scrypt in place of SHA256 in its
proof-of-work, with the intention of being ``ASIC-resistant'' in order to allow
anyone to mine competitively with only a CPU~\cite{litecoin}.

Permacoin is a proposed altcoin that uses a novel
\emph{proof-of-storage}~\cite{permacoin}.  Rather than waste computational
resources solving a useless proof-of-work puzzle (as in Bitcoin), miners are
instead incentivized to store parts of a large agreed-upon file. In order to be
competitive in Permacoin, miners prove that they can retreive an assigned
portion of the file.

@@

TorPath proposes a proof-of-bandwidth altcoin that incentivizes users to
participate in the Tor Network~\cite{torpath}. However, it relies on a set of
semi-trusted centralized servers to assign Tor circuits to clients. It is also
susceptible to collusion and sybil attacks by participants, however many of
these attacks are outside the threat model of TorPath as it requires performing
those attacks against the underlying Tor network. In contrast, DDoSCoin does not
require any centralized parties for the proof-of-DDoS, besides trusting existing
certificate authorities to validate domains.

Although Bitcoin uses a scripting language for transactions (see
Section~\ref{sec:scripting}), the allowed operations are very
limited~\cite{bitcoin-paper}. Ethereum allows transactions to be
\emph{programmable contracts}, whereby a programmer can specify in a custom
scripting language arbitrary logic, including conditional payments or
fee-collection. While the Ethereum Virtual Machine (EVM) that executes these
contracts does not provide external network access to the scripts, it could
still be used to implement some parts of DDoSCoin. For example, it is possible
to create an Ethereum contract that pays a bounty to anyone that can provide a
proof-of-DDoS for a specified target. This would effectively accomplish the same
outcome as PAY\_TO\_DDOS (described in Section~\ref{sec:pay-to-ddos}), and
implementing DDoSCoin's proof-of-DDoS verification.

@@

Bitcoin employs a hash-based proof-of-work protocol to construct a public ledger
of transactions. In this protocol, miners attempt to solve a simple hash-based
computational puzzle in order to mine blocks. Mining a block nets the miner a
reward, and the right to specify what new (valid) transactions should be
included in the public ledger. To mine a block, a miner must find a hash of a
block header that is less than an adjustable target. The block header includes
the hash of the last block found, the Merkle root of the list of transactions
the miner wants to include in this block, and a nonce. The easiest way to solve
this puzzle is to iterate the nonce\footnote{or modify transactions, therby
changing the Merkle root} until the hash satisfies the target difficulty. Then,
the miner publishes the found block, and miners use this block as the latest
block.

Each block commits to a set of transactions, which each must be valid for the
block to be considered valid. Transactions in Bitcoin are scripts, and each new
transactions specifies an \emph{output script} that must be satisfied in order
for the coins
to be spent. For example, an output script might specify that it requires a
spending transaction to provide a valid signature, with the output script
specifying the public key to validate it with. To spend such a transaction
requires creating a new transaction that references the previous one, and
provides an input (scriptSig) that ``solves'' the previous transactions' output
(scriptPubKey); in this case, a valid signature over the new transaction. This
new transaction can then specify a new output (scriptPubKey) for these coins.
Figure~\ref{fig:bitcoin-tx} shows an example of a standard Bitcoin transaction
script.

@@

Peercoin's proof-of-stake allows currency holders to mint new blocks based on
how many coin-days they are able and willing to consume. ``Coin-days consumed''
is a measure of the product of the amount of coins spent in a transaction, and
the number of days since they were last spent. For example, to consume 10
coin-days, a currency holder can spend 10 Peercoin that they have held for a
day, or equivalently, spend 5 Peercoins that were last spent 2 days ago. Note
that the holder can send these coins to anyone (including themselves) in order
to consume the coin age.

To mint a new block, a minter creates a special transaction (presumably one
where the minter pays themself) where one of the inputs has been unspent for at
least 30 days. The resulting transaction, along with a timestamp, must meet a
certain hash target that gets easier proportional to how many coin-days are
consumed by the transaction. For example, if the current difficulty gives a
minter consuming 100 coin-days a 1\% chance of minting a block per second, a
minter that was able to consume 200 coin-days would have a 2\% chance per
second.

The input to the hash includes information about the ``aged'' transaction, as
well as a current timestamp\footnote{In recent versions of Peercoin, the hash
also includes a stakeModifier which is computed from recent blocks; however,
these details are not important for our purposes}. If this hash is less than the
current target multiplied by the number of coin-days consumed in the
transaction, then the transaction meets the proof-of-stake difficulty and a new
block is minted. Although this looks similar to a proof-of-work check where a
hash is being compared to a target, here the only varying inputs are the
long-lived (aged) input transaction, and a course-grained timestamp with a
resolution of 1 second. Thus, for each aged unspent transaction output they
control, minters perform only one hash per second in order to solve the
proof-of-stake.

@@

to generate the 32-byte \texttt{client\_random}, where $prev\_block$ is
the SHA256 hash of the previous block header, $merkle\_root$ is the
Merkle root of transactions (as computed in Bitcoin), and $N$ is the random nonce.

@@

Next, the server sends its certificate chain, and a server key exchange message.
The certificate chain contains the server's (signed) TLS certificate, as well as
intermediate certificate authorities (CAs) that create a signature chain to a
browser-trusted root CA. Inside the server's certificate is a public
key, as well as the identity of the server (i.e. it's domain). The miner stores
these for verification in case a block is found.

In the server key exchange message, the server sends key exchange parameters
(such as the Diffie-Hellman parameters and the ephemeral public value generated
by the server, or the curve parameters and a public curve point in ECDHE). The
server signs these key exchange parameters, along with the
\texttt{client\_random} and \texttt{server\_random}. This signature can be
verified with the public key in the certificate.

Because the server key exchange signature contains the \texttt{client\_random}
and \texttt{server\_random}, the signature value will be unpredictable to the
client ahead of time. In addition, each signature will be a random value that
depends on the miner-provided nonce. Thus, it can be used as a proof-of-work in the
following way:

@@

As an aside, this interesting property gives rise to an observation that with respect to
clients, the contents of TLS connections are \emph{deniable}. That is, it is not
possible for a client to record a TLS connection (including its chosen secrets)
and report this to a third party in a way that cryptographically proves what the
server says. This property has been accomplished in different more efficient ways in various
secure messaging protocols such as Off-the-Record (OTR)~\cite{otr}.

Besides TLS 1.2, there are other cryptographic protocols that include the server
signing a client-chosen value. For example, the SSH protocol key exchange
involves the server signing a hash over the previous handshake messages,
including the client-provided identification (version) string, and
Diffie-Hellman public value~\cite{rfc4253}. Either of these fields could be used
to encode the necessary commitments (previous block, Merkle root, and nonce)
used in DDoSCoin.  However, SSH server identities are generally not signed by a
trusted party, making verification that a miner has communicated with a
particular server more complicated.  Nonetheless, identities in an SSH-based
DDoSCoin could simply be the server's host key rather than a domain in a
CA-signed certificate.

@@

If DDoSCoin accepted proofs against any TLS 1.2 server, miners would be
incentivized to set up their own TLS servers locally, and focus exclusively on
``attacking'' those servers instead of remote ones. Since the miner would have
access to the private key for that server, they would not be required to even
create network connections, leading to the proof-of-work being a computational
puzzle rather than one based on participation in a denial of service over a
network.
To prevent this, DDoSCoin must have a way to agree on which victims are
acceptable targets for the proofs-of-DDoS to be considered valid. Similarly, it
is important to focus the denial-of-service effort toward a single or small
number of victims in order to have the most impact.

@@

To address these issues, we propose two mechanisms that DDoSCoin can
employ to allow victims to be selected by consensus. The first mechanism allows
anyone to commit money to whoever can prove they sent an amount of traffic to a target
(PAY\_TO\_DDOS). The second allows for updating the list of victim domains that
miners are allowed to attack when mining for blocks.

@@

In order to allow victims to be (temporarily) selected for DoS, DDoSCoin allows
``bounties'' for targeting specific servers. To accomplish this, DDoSCoin
introduces a new payment opcode, PAY\_TO\_DDOS, that can be used in transactions
subject to certain constraints. This opcode takes two arguments in an output
script: a string representing a domain name that the payer wishes to have
DDoSed, and a target difficulty corresponding to the amount of connections the
payer wishes to be made. Once this transaction is stored in a valid block,
anyone can collect its reward by creating a connection to the specified victim
server and obtaining a response that meets the given target difficulty. These
connections are made similar to the way that miners connect to victim servers to
create blocks, but with a few important differences. First, the
\texttt{client\_random} is generated as follows:
\begin{equation}
SHA256(txid || output\_script || N)
\end{equation}

@@

Since PAY\_TO\_DDOS transactions can be claimed by anyone, there is a risk to
the collector that by the time they complete their DoS attack, someone else will
have collected the payment. Any target specified by a PAY\_TO\_DDOS transaction
could use their priveleged position to turn the proof-of-work into a computational challenge.
Since the challenge is no longer bound by the network, the target can claim the reward for
themselves. Quickly solved PAY\_TO\_DDOS transactions with no degradation of service
would indicate to the actor providing the bounty that the target is claiming its own bounty.

@@

In order to allow the victim list to be updated dynamically, DDoSCoin uses
\emph{Proof-of-Stake} to let currency holders make small changes to the list of
acceptable victim domains. Using proof-of-stake ensures that updates are only
done by actors that already have a substantial stake in the currency, either by
purchasing it or by previously participating in the (DoS) mining themselves.

To update the list, a currency holder ``mints'' a proof-of-stake transaction
similar to Peercoin. First, they must hold a number of coins that have been
unspent for more than 30 days. After the 30 days have passed, each second the
minter
hashes the aged transaction, a recent stake-modifier block, and a current
(seconds-resolution) timestamp. If this hash is less than the current
proof-of-stake target difficulty multiplied by the coin-age being consumed in
this transaction, then the currency holder is allowed to make a new
proof-of-stake block. Inside this block, the currency holder can make one
addition to (or one deletion from) the current victim list.

@@

After this block has been published, miners must wait until 10 proof-of-DoS
(non-proof-of-stake) blocks have been mined with the old list of valid domains
before the specified delta to the change list is applied. This discourages
malicious miners from forking the chain at an earlier block with a
proof-of-stake block adding their local domain to the victim list, and
immediately mining blocks on top of it to catch up to the main chain.

@@

Many positive results have come from cryptocurrencies.
Bitcoin was invented with the goal of creating a decentralized digital currency, 
and to that end has been more sucessful than most imagined. Banks are turning
to ``Blockchain technology'' to solve issues regarding public ledgers.
Primecoin and TorPath use cryptocurrencies to incentivize positive actions.
However, this positivity is not inherent to cryptocurrencies. DDoSCoin demonstrates
malicousness inherent to a currency's design, turning the notion of what constitutes
a ``useful'' proof-of-work on its head. Certainly a DDoS attack it useful to someone,
but negatively impacts society as a whole.

DDoSCoin uses proof that the miner connected to a given server a sufficient number 
of times as its proof-of-work. This is an indirect measurement of how much bandwidth
to a given endpoint is being wasted by the miner. This provides a unique challenge
when miners have different bandwidths to that given endpoint. The extreme of 
having a different bandwidth is being the target, and having the private key 
for the site. Having this priveleged position allows 
the target to actively engage in DDoSCoin as a defense. We discuss this further in
Section~\ref{sec:defense}.

An interesting choice in the design of DDoSCoin is target-setting is done 
dynamically, and by consensus. A given target can go offline, or in some other way
defend against DDoSCoin at any point. When this happens, the currency cannot stall,
as then no coins could be transacted. This necessitates dynamic target-setting, 
despite how strange it may be to have the ``goalposts'' move on miners. This places
risk in targetting sites that are likely to be removed from the target list, or
\emph{controversial} sites. However, each site has its difficulty adjusted 
individually, the controversial site will be easier to mine a block from as more 
miners shy away, balancing the affect.

@@

\subsection{Ethical Considerations}
%¯\\\_(ツ)\_/¯
%\symbol{2544}
While we acknowlege this work introduces an idea that could be used to incentivize 
malicous behavior, the ethics of this paper are controlled. We only demonstrate a 
proof of concept, and in doing so, only attack websites we have ownership of.
Further, we do not publish the full coin, and keep the source of our proof-of-concept
closed. We believe it important to fully disclose potential attacks, even those that
require the development of an altcoin to execute. This is especially important in the
face of the impending commitment to the design of TLS 1.3, and compounded by how long 
TLS/SSL protocol versions stay in active use. Further, proof-of-DDoS has applications 
beyond just DDoSCoin.

>>>>

In this paper, we present DDoSCoin, which is a cryptocurrency with a
\emph{malicious} proof-of-work. DDoSCoin allows miners to prove that they have
contributed to a distributed denial of service attack against specific target
servers.  This proof involves making a large number of TLS connections to a
target server, and using cryptographic responses to prove that a
large number of connections has been made. Like proof-of-work puzzles, these
proofs are inexpensive to verify, and can be made arbitrarily difficult to
solve.

@@

Cryptocurrencies rely on proofs-of-work that require miners to spend a
large amount of effort to solve a specific puzzle.  Solutions to these puzzles,
on the other hand, are designed to be inexpensive to verify. In Bitcoin, the
proof-of-work is a computational puzzle based on the SHA256 hash function, and
miners are tasked with finding a partial preimage. The best way to do this is to
iterate over a large number of inputs to the hash function, and check if the
output hash satisfies the partial preimage target. In simplified terms, to find
an input that hashes to N bits of 0s, the miner must perform on average $2^{N}$
hashes. Once such an input is found, other miners and Bitcoin nodes can verify the
puzzle solution with a single hash~\footnote{Bitcoin uses double-SHA256 in its
design, but this detail is not important for the purposes of this paper.}.

@@

Many see this distributed computation as a colossal waste of CPU resources, and
researchers have proposed alternative cryptocurrencies, or altcoins, that aim to
have more beneficial proofs-of-work~\cite{primecoin,permacoin} that provide
utility beyond securing the underlying currency: finding chains of
large primes or proving the archive of data. In this paper however, we
investigate going in the opposite direction, and propose an altcoin that has a
\emph{malicious} proof-of-work that is externally detrimental.

In particular, we propose a proof-of-work that allows miners to prove they have
participated in a distributed denial of service, or DDoS, attack against a
particular target. Miners are incentivized to send and receive large amounts of network
traffic to and from the target in order to produce a valid proof-of-work. As in other
cryptocurrencies, these proofs can be inexpensively verified by others, and the
original miner can collect a reward. This reward can be sold for other
currencies, including Bitcoin or even traditional currencies, allowing botnet
owners and other attacks to directly collect revenue for their assistance
in a decentralized DDoS attack.

The malicious ``proof-of-DDoS'' operates by having miners create a large number of
TLS connections to a target webserver, and using the server's signed responses
as a proof of connection. In modern versions of TLS, the server signs a
client-provided parameter of the connection, along with server-provided values
used in the key exchange of the connection. This allows the client to prove to
others that it has communicated with the server. In addition, the signed value
returned by the server is not predictable to the client, and is randomly
distributed. Thus, clients can use a similar trick to those in Bitcoin, and only
report connections that match some rare threshold, such as the signature from
the server starts with $N$ bits of 0s. On average, it will take clients $2^{N}$
connections to produce such a proof.

@@

\emph{Contributions}
\begin{itemize}
\item Propose a novel conceptual cryptocurrency, DDoSCoin, whose proof-of-work
incentives miners to participate in a DDoS attack, and allows them prove they have done so
\item Describe a way for target victims to be chosen by consensus of its
participants
\item Implement our proof-of-work function and evaluate its performance and
impact
\item Discuss several defenses against such a cryptocurrency that potential
victims can employ
\end{itemize}

@@

Many alternate cryptocurrency protocols have been proposed since the
creation of Bitcoin. Although none have yet eclipsed the popularity of Bitcoin,
many altcoins have interesting innovations, often in the form of alternate
proof-of-work. For example, Litecoin uses scrypt in place of SHA256 in its
proof-of-work, with the intention of being ``ASIC-resistant'' in order to allow
anyone to mine competitively with only a CPU~\cite{litecoin}.

Permacoin is a proposed altcoin that uses a novel
\emph{proof-of-storage}~\cite{permacoin}.  Rather than waste computational
resources solving a useless proof-of-work puzzle, such as in Bitcoin, miners are
instead incentivized to store parts of a large agreed-upon file. In order to be
competitive in Permacoin, miners prove that they can retreive an assigned
portion of the file.

@@

TorPath proposes a proof-of-bandwidth altcoin that incentivizes users to
participate in the Tor Network~\cite{torpath}. However, it relies on a set of
semi-trusted centralized servers to assign Tor circuits to clients. It is also
susceptible to collusion and sybil attacks by participants, however many of
these attacks are outside the threat model of TorPath, as it requires performing
those attacks against the underlying Tor network. In contrast, DDoSCoin does not
require any centralized parties for the proof-of-DDoS, besides trusting existing
certificate authorities to validate domains.

Although Bitcoin uses a scripting language for transactions (see
Section~\ref{sec:scripting}), the allowed operations are very
limited~\cite{bitcoin-paper}. Ethereum allows transactions to be
\emph{programmable contracts}, whereby a transaction can be specified in a custom
scripting language with arbitrary logic, including conditional payments or
fee-collection. While the Ethereum Virtual Machine that executes these
contracts does not provide external network access to the scripts, it could
still be used to implement some parts of DDoSCoin. For example, it is possible
to create an Ethereum contract that pays a bounty to anyone that can provide a
proof-of-DDoS for a specified target. This would effectively accomplish the same
outcome as PAY\_TO\_DDOS (described in Section~\ref{sec:pay-to-ddos}), and
implementing DDoSCoin's proof-of-DDoS verification.

@@

Bitcoin employs a hash-based proof-of-work protocol to construct a public ledger
of transactions. In this protocol, miners attempt to solve a simple hash-based
computational puzzle in order to mine blocks. Mining a block nets the miner a
reward and the right to specify what new, valid transactions should be
included in the public ledger. To mine a block, a miner must find a hash of a
block header that is less than an adjustable target. The block header includes
the hash of the last block found, the Merkle root of the list of transactions
the miner wants to include in this block, and a nonce. The easiest way to solve
this puzzle is to iterate the nonce\footnote{or modify transactions, therby
changing the Merkle root} until the hash satisfies the target difficulty. Then,
the miner publishes the found block, and miners use this block as the latest
block.

Each block commits to a set of transactions, which each must be valid for the
block to be considered valid. Transactions in Bitcoin are scripts, and each new
transaction specifies an \emph{output script} that must be satisfied in order
for the coins
to be spent. For example, an output script might specify that it requires a
spending transaction to provide a valid signature, with the output script
specifying the public key to validate it with. To spend such a transaction
requires creating a new transaction that references the previous one, and
provides an input (scriptSig) that ``solves'' the previous transactions' output
(scriptPubKey). In this case, a valid signature over the new transaction. This
new transaction can then specify a new output (scriptPubKey) for these coins.
Figure~\ref{fig:bitcoin-tx} shows an example of a standard Bitcoin transaction
script.

@@

Peercoin's proof-of-stake allows currency holders to mint new blocks based on
how many coin-days they are able and willing to consume. ``Coin-days consumed''
is a measure of the product of the amount of coins spent in a transaction, and
the number of days since they were last spent. For example, to consume 10
coin-days, a currency holder can spend 10 Peercoin that they have held for a
day, or equivalently, spend 5 Peercoins that were last spent 2 days ago. Note
that the holder can send these coins to anyone, including themselves, in order
to consume the coin age.

To mint a new block, a minter creates a special transaction, presumably one
where the minter pays themself, where one of the inputs has been unspent for at
least 30 days. The resulting transaction, along with a timestamp, must meet a
certain hash target that gets easier proportional to how many coin-days are
consumed by the transaction. For example, if the current difficulty gives a
minter consuming 100 coin-days a 1\% chance of minting a block per second, a
minter that was able to consume 200 coin-days would have a 2\% chance per
second.

The input to the hash includes information about the ``aged'' transaction, as
well as a current timestamp\footnote{In recent versions of Peercoin, the hash
also includes a stakeModifier which is computed from recent blocks; however,
these details are not important for our purposes}. If this hash is less than the
current target multiplied by the number of coin-days consumed in the
transaction, then the transaction meets the proof-of-stake difficulty and a new
block is minted. Although this looks similar to a proof-of-work check where a
hash is being compared to a target, here the only varying inputs are the
long-lived input transaction, and a course-grained timestamp with a
resolution of 1 second. Thus, for each aged unspent transaction output they
control, minters perform only one hash per second in order to solve the
proof-of-stake.

@@

to generate the 32-byte \texttt{client\_random}, where $prev\_block$ is
the SHA256 hash of the previous block header, $merkle\_root$ is the
Merkle root of transactions as computed in Bitcoin, and $N$ is the random nonce.

@@

Next, the server sends its certificate chain, and a server key exchange message.
The certificate chain contains the server's signed TLS certificate, as well as
intermediate certificate authorities that create a signature chain to a
browser-trusted root CA. Inside the server's certificate is a public
key, as well as the identity of the server represented by it's domain. The miner stores
these for verification in case a block is found.

In the server key exchange message, the server sends key exchange parameters
such as the Diffie-Hellman parameters and the ephemeral public value generated
by the server, or the curve parameters and a public curve point in ECDHE. The
server signs these key exchange parameters, along with the
\texttt{client\_random} and \texttt{server\_random}. This signature can be
verified with the public key in the certificate.

Since the server key exchange signature contains the \texttt{client\_random}
and \texttt{server\_random}, the signature value will be unpredictable to the
client ahead of time. In addition, each signature will be a random value that
depends on the miner-provided nonce. Thus, it can be used as a proof-of-work.

@@

As an aside, this interesting property gives rise to an observation that with respect to
clients, the contents of TLS connections are \emph{deniable}. That is, it is not
possible for a client to record a TLS connection, including its chosen secrets,
and report this to a third party in a way that cryptographically proves what the
server says. This property has been accomplished in different more efficient ways in various
secure messaging protocols such as Off-the-Record (OTR)~\cite{otr}.

Besides TLS 1.2, there are other cryptographic protocols that involve the server
signing a client-chosen value. For example, the SSH protocol key exchange
involves the server signing a hash over the previous handshake messages,
including the client-provided identification (version) string, and
Diffie-Hellman public value~\cite{rfc4253}. Either of these fields could be used
to encode the necessary commitments (previous block, Merkle root, and nonce)
used in DDoSCoin.  However, SSH server identities are generally not signed by a
trusted party, making verification that a miner has communicated with a
particular server more challenging.  Nonetheless, identities in an SSH-based
DDoSCoin could simply be the server's host key rather than a domain in a
CA-signed certificate.

@@

If DDoSCoin accepted proofs against any TLS 1.2 server, miners would be
incentivized to set up their own TLS servers locally, and focus exclusively on
``attacking'' those servers instead of remote ones. Since the miner would have
access to the private key for that server, they would not be required to even
create network connections, reducing the proof-of-work to a computational
puzzle rather than one based on participation in a denial of service over a
network.
To prevent this, DDoSCoin must have a way to agree on which victims are
acceptable targets for the proofs-of-DDoS to be considered valid. Similarly, it
is important to focus the denial-of-service effort toward a small
number of victims in order to have the most impact.

@@

To address these issues, we propose two mechanisms that DDoSCoin can
employ to allow victims to be selected by consensus. The first mechanism allows
anyone to commit DDoSCoins to whoever can prove they sent an amount of traffic to a target
(PAY\_TO\_DDOS). The second allows for updating the list of victim domains that
miners are allowed to attack when mining for blocks.

@@

In order to allow victims to be (temporarily) selected for DoS, DDoSCoin allows
``bounties'' for targeting specific servers. To accomplish this, DDoSCoin
introduces a new payment opcode, PAY\_TO\_DDOS, that can be used in transactions
subject to certain constraints. This opcode takes two arguments in an output
script: a string representing a domain name that the payer wishes to have
DDoSed, and a target difficulty corresponding to the amount of connections the
payer wishes to be made. Once this transaction is stored in a valid block,
anyone can collect its reward by creating a connection to the specified victim
server and obtaining a response that meets the given target difficulty. These
connections are made similar to how miners connect to victim servers to
create blocks, but with a few important differences. First, the
\texttt{client\_random} is generated as follows:
\begin{equation}
SHA256(txid || output\_script || N)
\end{equation}

@@

Since PAY\_TO\_DDOS transactions can be claimed by anyone, there is a risk to
the collector that by the time they complete their DoS attack, someone else will
have collected the payment. Any target specified by a PAY\_TO\_DDOS transaction
could use their priveleged position to turn the proof-of-work into a computational challenge.
Since the challenge is no longer bound by the network, the target can claim the reward for
themselves. Quickly solved PAY\_TO\_DDOS transactions with no degradation of service
and sufficiently difficult proof-of-work
would indicate to the bounty provider that the target is claiming its bounty.

@@

In order to allow the victim list to be updated dynamically, DDoSCoin uses
\emph{Proof-of-Stake} to let currency holders make small changes to the list of
acceptable victim domains. Using proof-of-stake ensures that updates are only
done by actors that already have a substantial stake in the currency, either by
purchasing it or by previously participating in the mining themselves.

To update the list, a currency holder ``mints'' a proof-of-stake transaction
similar to Peercoin. First, they must hold a number of coins that have been
unspent for more than 30 days. After the 30 days have passed, each second the
minter
hashes the aged transaction, a recent stake-modifier block, and a current
seconds-resolution timestamp. If this hash is less than the current
proof-of-stake target difficulty multiplied by the coin-age being consumed in
this transaction, then the currency holder is allowed to make a new
proof-of-stake block. Inside this block, the currency holder can make one
addition to or one deletion from the current victim list.

@@

After this block has been published, miners must wait until 10 proof-of-DoS
blocks have been mined with the old list of valid domains
before the specified delta to the change list is applied. This discourages
malicious miners from forking the chain at an earlier block with a
proof-of-stake block adding their local domain to the victim list, and
immediately mining blocks on top of it to catch up to the main chain.

@@

Many positive results have come from cryptocurrencies.
Bitcoin was invented with the goal of creating a decentralized digital currency, 
and to that end has been more sucessful than most imagined. Banks are turning
to ``Blockchain technology'' to solve issues regarding public ledgers.
Primecoin and TorPath use cryptocurrencies to incentivize positive actions.
However, this positivity is not inherent to cryptocurrencies. DDoSCoin demonstrates
malicousness inherent to a currency's design, turning the notion of what constitutes
a ``useful'' proof-of-work around. Certainly a DDoS attack it useful to someone,
but negatively impacts society as a whole.

DDoSCoin uses proof that the miner connected to a given server a sufficient number 
of times as its proof-of-work. This is an indirect measurement of how much bandwidth
to a given endpoint is being wasted by the miner. This provides a unique challenge
to the currency 
when miners have different bandwidths to that given endpoint. The extreme of 
having a different bandwidth is being the target, and having the private key 
for the site. Having this priveleged position allows 
the target to actively engage in DDoSCoin as a defense. We discuss this further in
Section~\ref{sec:defense}.

An interesting choice in the design of DDoSCoin is target-setting is done 
dynamically, and by consensus. A given target can go offline, or in some other way
defend against DDoSCoin at any point. When this happens, the currency cannot stall,
as then no coins could be transacted. This necessitates dynamic target-setting.

@@

\subsection{Ethical Considerations}
%¯\\\_(ツ)\_/¯
%\symbol{2544}
While we acknowlege this work introduces an idea that could be used to incentivize 
malicous behavior, the ethics of this paper are controlled. We only demonstrate a 
proof of concept, and in doing so, only attack websites we have ownership of.
Further, we do not publish the full coin.
We believe it important to fully disclose potential attacks, even those that
require the development of an altcoin to execute. This is especially important in the
face of the impending commitment to the design of TLS 1.3, and compounded by how long 
TLS/SSL protocol versions stay in active use. Further, proof-of-DDoS has applications 
beyond just DDoSCoin.
